Temporal Dynamics of Normalization Reweighting

### 2022-10-01 manuscript.Rmd
Added code for automatically downloading data from OSF

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires XGB of storage)
# 2 - download processed individual data and analyse (requires XGB of storage)
# 3 - download all raw data and analyse (requires XGB of storage)

@@

scoreAQshort <- function(qdata){
# score the AQ questionnaire - short version
# input is a row from a spreadsheet indicating responses to 28 questions
AQanswers <- toupper(c('(1) Definitely agree','(2) Slightly agree', '(3) Slightly disagree', '(4) Definitely disagree'))
reverseitems <- rep(0,28)
 # reverse scored questionnaire items
reverseitems[c(7, 50, 52, 54, 55, 58, 59, 62, 63, 64, 65, 66, 67, 69, 72)] <- 1

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}

@@

hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)

@@

osfnode <- 'y4n5k'    # this is where the pilot data are stored
osfproject <- osf_retrieve_node(osfnode)
EEGfiles <- osf_ls_files(osfproject,n_max=300)

datadir <- 'temp/raw/'
tempdir <- 'temp/raw/temp/'

hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
subjcounter <- 0

@@

    if (s < 10){tarname <- paste0('S0', s, '.tar')}
    if (s > 9){tarname <- paste0('S', s, '.tar')}

    if (!file.exists(paste0(datadir,tarname))){
      fid <- which(EEGfiles$name==tarname)
      osf_download(EEGfiles[fid,],datadir,progress=TRUE)
    }

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))

    untar(paste0(datadir,tarname),exdir=tempdir)

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    if (s < 10){d <- dir(path = paste0(tempdir,'S0',s), pattern='*.csv.gz',full.names=TRUE)}
    if (s > 9){d <- dir(path = paste0(tempdir,'S',s), pattern='*.csv.gz',full.names=TRUE)}

    d <- dir(path = tempdir, pattern = '*.csv.gz')

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
      for (n in 1500:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
      }
      }

@@

    for (block in 1:length(d)){file.remove(d[block])}

@@

d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
EEGtimecourse <- array(0,dim=c(length(d),length(findex),3,13000))
EEGspectra <- array(0,dim=c(length(d),3,20*10))
EEGscalpresps <- array(0,dim=c(length(d),4,14,64))
EEGallconds <- array(0,dim=c(length(d),4,14))
alltrialcounts <- array(0,dim=c(length(d),14,64))

@@

load('temp/Pilotsummary.RData')

@@

We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window. The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue). Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b). The reduction in signal strength when the mask component is added illustrates the masking effect.

@@

      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
    }

@@

d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
EEGtimecourse5Hz <- array(0,dim=c(length(d),4,8000))
EEGtimecourse7Hz <- array(0,dim=c(length(d),4,8000))
allwaves <- array(0,dim=c(length(d),4,9000))
allspec <- array(0,dim=c(length(d),4,duration*20))
allheads5 <- array(0,dim=c(length(d),4,64))
allheads7 <- array(0,dim=c(length(d),4,64))
EEGtrialsincluded <- array(0,dim=c(length(d),4,64))
allAQ <- NULL
allSPQ <- NULL
for (s in 1:length(d)){
  load(d[s])
  targetchannels <- match(targetelectrodes, electrodes) - 2
  EEGtrialsincluded[s,,] <- trialsincluded
  for (cond in 1:4){
    temp <- rowMeans(subjwaves[cond,,targetchannels],na.rm=TRUE)
    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    # temp[nainds] <- (temp[nainds-1] + temp[nainds+1])/2   # interpolate adjacent values
    temp[nainds] <- 0   # replace with zeros
    allwaves[s,cond,] <- temp - mean(temp)
    spec <- fft(temp[1501:7500])/6000
    allspec[s,cond,] <- spec[1+(1:(duration*20))]

@@

@@

  d <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=TRUE)
  d2 <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=FALSE)

  MEGtimecourse5Hz <- array(0,dim=c(length(d),4,8008))
  MEGtimecourse7Hz <- array(0,dim=c(length(d),4,8008))
  # allwaves <- array(0,dim=c(length(d),4,9009))
  allspec <- array(0,dim=c(length(d),4,duration*20))
  allRnos <- NULL
  for (s in 1:length(d)){
    allRnos[s] <- substr(d2[s],1,5)
    data <- readMat(d[s])

      for (cond in 1:4){
        temp <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],],na.rm=TRUE)
        nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
        temp[nainds] <- 0   # replace with zeros
        # allwaves[s,cond,] <- temp - mean(temp)
        spec <- fft(temp[1501:7500])/6000
        allspec[s,cond,] <- spec[1+(1:(duration*20))]

        fspec1 <- NULL
        fspec2 <- NULL
        for (t in 1:(9009-binwidth)){
          spec <- fft(temp[t:(t+binwidth-1)])/binwidth
          fspec1[t] <- spec[tindex]
          fspec2[t] <- spec[mindex]
        }
        MEGtimecourse5Hz[s,cond,] <- fspec1
        MEGtimecourse7Hz[s,cond,] <- fspec2

@@

  save(file='temp/MEGsummaryV1.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))

@@

if (processdata>0){
  load('temp/MEGsummaryV1.RData')

@@

      meanspec[cond,] <- colMeans(abs(allspec[which(isincluded[cond,]==1),cond,]),na.rm=TRUE)
      # meanwave[area,cond,] <- colMeans(allwaves[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE)
    }

@@

    # spl7a <- smooth.spline(times,MEGmeantime7Hz[1,],df=20)
    # lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)

@@

  e1 <- readTIFF('temp/groupbrainbothSNR.tif')
  e2 <- readTIFF('temp/LH.tif')
  e3 <- readTIFF('temp/RH.tif')

@@

  # text(-0.02,0.89,'5Hz',pos=4,cex=2)
  # text(-0.02,0.61,'7Hz',pos=4,cex=2)

@@

pilotAQ <- read.csv('temp/AQscores.csv',header=FALSE)
pilotAQ <- pilotAQ[-75,2]

load("temp/questionnairedataMSci.RData")
MEGAQ <- qdata$AQ[1:19]
MEGgroup <- qdata$Diagnosis[1:19]

@@

t_age <- t.test(qdata$Age[which(qdata$Diagnosis=='Yes')],qdata$Age[which(qdata$Diagnosis=='No')],paired=FALSE,var.equal=TRUE)

corMEG <- cor.test(qdata$AQ[1:19],qdata$SPQ[1:19])
corEEG <- cor.test(allAQ,allSPQ)

@@

  load('temp/MEGsummaryV1.RData')
  MEGgroup <- qdata$Diagnosis
  MEGID <- qdata$ID
  dataorder <- match(MEGID,allRnos)
  # dataorder tells us the indices into the MEG data for each AQ score

@@

  CONindices <- dataorder[which(MEGgroup=='No')]
  ASCindices <- dataorder[which(MEGgroup=='Yes')]
  isCON <- (1:20)*0
  isASC <- (1:20)*0
  isCON[CONindices] <- 1
  isASC[ASCindices] <- 1

@@

To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data. Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups. The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data, consistent with previous results for the general population [@Baron-Cohen2001]. In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).

@@

EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox [@Delorme2004], and converted into a compressed ASCII format. Primary data analysis was then conducted using a bespoke _R_ script. In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform. We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021]. This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 3. Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant. We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio. These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons. For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.

For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011]. Structural MRI scans were processed using Freesurfer [@Dale1999] to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment. The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of @Wang2015. These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.

>>>>

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires XGB of storage)
# 2 - download processed individual data and analyse (requires XGB of storage)
# 3 - download all raw data and analyse (requires 78+GB of storage)

@@

scoreAQshort <- function(qdata){
# score the AQ questionnaire - short version
# input is a row from a spreadsheet indicating responses to 28 questions
AQanswers <- toupper(c('(4) Definitely agree','(3) Slightly agree', '(2) Slightly disagree', '(1) Definitely disagree'))
reverseitems <- rep(1,28)
 # reverse scored questionnaire items
reverseitems[c(3,5,8,11,12,19,21,22,24,25,26,27,28)] <- 0

@@

# check if directories exist to store data files (ignored by git)
if (!dir.exists('temp/')){dir.create('temp/')}
if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}
if (!dir.exists('temp/pilotraw/')){dir.create('temp/pilotraw/')}
if (!dir.exists('temp/pilotraw/temp/')){dir.create('temp/pilotraw/temp/')}

@@

osfproject <- osf_retrieve_node("ab3yv")
componentlist <- osf_ls_nodes(osfproject)
osffiles <- osf_ls_files(osfproject,n_max=300)

pilotproject <- osf_retrieve_node("y4n5k")
pilotfiles <- osf_ls_files(pilotproject,n_max=300)
if (!file.exists('temp/headerfile.csv')){
  hid <- pmatch('headerfile.csv',as.character(unlist(pilotfiles[,1])))
  osf_download(pilotfiles[hid,], path='temp/')
}
hdata <- read.csv('temp/headerfile.csv')

@@

datadir <- 'temp/pilotraw/'

legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
subjcounter <- 0

@@

    if (s < 10){subname <- paste0('S0', s)}
    if (s > 9){subname <- paste0('S', s)}

    tarname <- paste0(subname,'.tar')

    if (!file.exists(paste0(datadir,tarname))){
      fid <- which(pilotfiles$name==tarname)
      osf_download(pilotfiles[fid,],datadir,progress=TRUE)
    }
    untar(paste0(datadir,tarname),exdir=paste0(datadir,subname))
    file.remove(paste0(datadir,tarname))  # delete after unpacking

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    d <- dir(path = paste0(datadir,subname), pattern='*.csv.gz',full.names=TRUE)

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
       # ignore triggers starting in the first 1000ms that generate an error
      for (n in 1500:nrow(EEGdata)) {   
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
      }
      }

@@

     # optionally delete the files after use
    # for (block in 1:length(d)){file.remove(d[block])}

@@

d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)

# download any missing data files from osf
if (length(d)<100){
  pilotrepo <- pmatch('Processed pilot data',as.character(unlist(componentlist[,1])))
  pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
  for (s in 1:length(pilotfiles)){
    if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
      osf_download(pilotfiles[s,],'temp/VilidaiteProcessed/',progress=TRUE)
    }
  }
}

d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)

EEGtimecourse <- array(0,dim=c(length(d),length(findex),3,13000))
EEGspectra <- array(0,dim=c(length(d),3,20*10))
EEGscalpresps <- array(0,dim=c(length(d),4,14,64))
EEGallconds <- array(0,dim=c(length(d),4,14))
alltrialcounts <- array(0,dim=c(length(d),14,64))

@@

      if (!file.exists('temp/Pilotsummary.RData')){
      hid <- pmatch('Pilotsummary.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
      }  
load('temp/Pilotsummary.RData')

@@

We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window. The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue). For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.). Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b). The reduction in signal strength when the mask component is added illustrates the masking effect.

@@

      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
    }
 }
}

@@

d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)

# download any missing data files from osf
if (length(d)<100){
  EEGrepo <- pmatch('Processed EEG data',as.character(unlist(componentlist[,1])))
  EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
  for (s in 1:length(EEGfiles)){
    if (!file.exists(paste0('temp/EEGProcessed/',EEGfiles[s,1]))){
      osf_download(EEGfiles[s,],'temp/EEGProcessed/',progress=TRUE)
    }
  }
}

d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)

EEGtimecourse5Hz <- array(0,dim=c(length(d),4,8000))
EEGtimecourse7Hz <- array(0,dim=c(length(d),4,8000))
allwaves <- array(0,dim=c(length(d),4,9000))
allspec <- array(0,dim=c(length(d),4,duration*20))
allheads5 <- array(0,dim=c(length(d),4,64))
allheads7 <- array(0,dim=c(length(d),4,64))
EEGtrialsincluded <- array(0,dim=c(length(d),4,64))
allAQ <- NULL
allSPQ <- NULL
for (s in 1:length(d)){
  load(d[s])
  targetchannels <- match(targetelectrodes, electrodes) - 2
  EEGtrialsincluded[s,,] <- trialsincluded
  for (cond in 1:4){
    temp <- rowMeans(subjwaves[cond,,targetchannels],na.rm=TRUE)
    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    # temp[nainds] <- (temp[nainds-1] + temp[nainds+1])/2   # interpolate adjacent values
    temp[nainds] <- 0   # replace with zeros
    allwaves[s,cond,] <- temp - mean(temp)
    spec <- fft(temp[1501:7500])/6000
    allspec[s,cond,] <- spec[1+(1:(duration*20))]

@@

 if (!file.exists('temp/EEGsummary.RData')){
      hid <- pmatch('EEGsummary.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }

@@

  d <- dir(path = 'temp/MEGdata/', pattern = '*data.RData', full.names=TRUE)

  # download any missing data files from osf
if (length(d)<20){
  MEGrepo <- pmatch('Processed MEG data',as.character(unlist(componentlist[,1])))
  MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
  for (s in 1:length(MEGfiles)){
    if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){
      osf_download(MEGfiles[s,],'temp/MEGdata/',progress=TRUE)
    }
  }
}

   d <- dir(path = 'temp/MEGdata/', pattern = '*data.RData', full.names=TRUE)

  MEGtimecourse5Hz <- array(0,dim=c(length(d),4,8008))
  MEGtimecourse7Hz <- array(0,dim=c(length(d),4,8008))
  MEGtrialsincluded <- matrix(0,nrow=20,ncol=4)
  MEGsubjwaves <- array(0,dim=c(length(d),4,9009))
  allspec <- array(0,dim=c(length(d),4,duration*20))
  MEGallAQ <- NULL
  MEGallSPQ <- NULL
  MEGallAge <- NULL
  MEGallGender <- NULL
  MEGallDiagnosis <- NULL
  for (s in 1:length(d)){

    load(d[s])

    MEGallAge[s] <- qdatasubj[1,1]
    MEGallGender[s] <- qdatasubj[1,2]
    MEGallDiagnosis[s] <- qdatasubj[1,3]
    if (qdatasubj[1,5]!=0){
    MEGallAQ[s] <- scoreAQ(qdatasubj[1,5:54])
    MEGallSPQ[s] <- scoreSPQ(qdatasubj[1,55:146])
    }
    if (qdatasubj[1,5]==0){MEGallAQ[s] <- 999
    MEGallSPQ[s] <- 999}

      for (cond in 1:4){

          temp <- alltrials[cond,1:trialcounter[1,cond],]
          spec5 <- NULL
          spec7 <- NULL
          for (t in 1:trialcounter[1,cond]){
            spec <- fft(temp[t,1501:7506])/6006
            spec5[t] <- spec[targetF*duration+1]
            spec7[t] <- spec[maskF*duration+1]
          }
        spec5[which(is.na(spec5))] <- 0
        spec7[which(is.na(spec7))] <- 0
      if (length(which(abs(spec5)>0))>2){  
      tempxy <- data.frame(Re(spec5),Im(spec5))
      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      tempxy <- data.frame(Re(spec7),Im(spec7))
      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
      i <- which(D5<3 & D7<3)
      MEGtrialsincluded[s,cond] <- length(i)
      temp <- colMeans(temp[i,])
      MEGsubjwaves[s,cond,] <- temp
      spec <- fft(temp[1501:7506])/6006
      allspec[s,cond,] <- spec[1+(1:(duration*20))]

        fspec1 <- NULL
        fspec2 <- NULL
        for (t in 1:(9009-binwidth)){
          spec <- fft(temp[t:(t+binwidth-1)])/binwidth
          fspec1[t] <- spec[tindex]
          fspec2[t] <- spec[mindex]
        }

        MEGtimecourse5Hz[s,cond,] <- fspec1
        MEGtimecourse7Hz[s,cond,] <- fspec2

@@

  save(file='temp/MEGsummary.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','MEGtrialsincluded','MEGallAge','MEGallGender','MEGallDiagnosis','MEGallAQ','MEGallSPQ'))

@@

 if (!file.exists('temp/MEGsummary.RData')){
      hid <- pmatch('MEGsummary.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }

load('temp/MEGsummary.RData')
MEGpercentexcluded <- 100 - (100*mean(MEGtrialsincluded)/48)

@@

      meanspec[cond,] <- colMeans(abs(allspec[which(isincluded[cond,]==1),cond,]),na.rm=TRUE)
    }

@@

@@

   if (!file.exists('temp/groupbrainbothSNR.tif')){
      hid <- pmatch('groupbrainbothSNR.tif',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
   }
   if (!file.exists('temp/LH.tif')){
      hid <- pmatch('LH.tif',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
   }
  if (!file.exists('temp/RH.tif')){
      hid <- pmatch('RH.tif',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
   }
  e1 <- readTIFF('temp/groupbrainbothSNR.tif')
  e2 <- readTIFF('temp/LH.tif')
  e3 <- readTIFF('temp/RH.tif')

@@

@@

 if (!file.exists('temp/EEGsummary.RData')){
      hid <- pmatch('EEGsummary.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
load('temp/EEGsummary.RData')

 if (!file.exists('temp/pilotquestionnaire.csv')){
      hid <- pmatch('pilotquestionnaire.csv',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
pilotqdata <- read.csv('temp/pilotquestionnaire.csv')
pilotAQ <- NULL
for (n in 1:101){
  pilotAQ[n] <- scoreAQshort(pilotqdata[n,3:30])
}
pilotAQ <- pilotAQ[-75]

 if (!file.exists('temp/MEGsummary.RData')){
      hid <- pmatch('MEGsummary.RData',as.character(unlist(osffiles[,1])))
      osf_download(osffiles[hid,],'temp/',progress=TRUE)
 }
load("temp/MEGsummary.RData")
MEGAQ <- MEGallAQ[2:20]
MEGgroup <- MEGallDiagnosis[2:20]

@@

t_age <- t.test(MEGallAge[which(MEGallDiagnosis=='Yes')],MEGallAge[which(MEGallDiagnosis=='No')],paired=FALSE,var.equal=TRUE)

corMEG <- cor.test(MEGallAQ[2:20],MEGallSPQ[2:20])
corEEG <- cor.test(allAQ,allSPQ)

@@

  load('temp/MEGsummary.RData')
  MEGgroup <- MEGallDiagnosis

@@

  CONindices <- which(MEGgroup=='No')
  ASCindices <- which(MEGgroup=='Yes')
  isCON <- (1:20)*0
  isASC <- (1:20)*0
  isCON[CONindices] <- 1
  isASC[ASCindices] <- 1

@@

To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data. Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups. The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data. In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group). These distributions are consistent with previous results for AQ [@Baron-Cohen2001].

@@

EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox [@Delorme2004], and converted into a compressed ASCII format. Primary data analysis was then conducted using a bespoke _R_ script. In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform. We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021]. This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2. Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant. We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio. These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons. For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.

For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011]. Structural MRI scans were processed using Freesurfer [@Dale1999] to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment. The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of @Wang2015. These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above. The outlier rejection procedure excluded `r round(MEGpercentexcluded,digits=2)`% of trials for Experiment 3.
